---
title: "Writing Data Frame & Plot Functions in R"
format: html
number-sections: true
number-depth: 2
bibliography: references.bib
editor: source
execute: 
  echo: true
  include: true
---

```{r}
#| include: false
#| echo: false

library(tidyverse)
library(lubridate)

```


<!-- Advanced R on lazy evaluation: https://adv-r.hadley.nz/functions.html#lazy-evaluation -->

<!-- What is data-masking and why do I need {{? -->
<!-- https://rlang.r-lib.org/reference/topic-data-mask.html -->

This week, we’re going to learn how to write our own dplyr-like
functions---functions that behave the way dplyr verbs do. To do this, we’ll dive
into some of the deeper ideas that power the tidyverse, 
especially how functions in dplyr interpret and evaluate code. These
ideas---collectively known as tidy evaluation---make the tidyverse so expressive 
and intuitive for common data-analysis tasks, but they can also make
programming with it more challenging.

This week, we’re moving from using tidyverse functions for "common" tasks to
learning how to build our own functions for the "less common" ones. By the end, 
you’ll understand not only how to use dplyr, but how to extend it.

By the end of the week you should have a grasp of:

-   What the "embracing" (`{{{ }}}`) operator is

-   How to use the `{{{ }}}` operator in data frame functions

-   Why we need to use the `{{{ }}}` operator when writing data frame functions

-   What "data masking" is 

-   What functions use data masking

-   What "tidy selection" is

-   What functions use tidy selection

-   How to use `across()` in functions

-   How to use `pick()` in functions

::: columns
::: {.column width="60%"}
#### 📖 Readings: 60-90 minutes

#### 📽 Watch Videos: 20 minutes
:::

::: {.column width="5%"}
:::

::: {.column width="35%"}
#### ✅  Preview Activities: 3
:::
:::

# Writing Data Frame Functions in R


Now that we've learned at a high level how to write functions that operate on a
we're going to take this a step further and learn how to work with "tidy 
evaluation." 

Since there isn't a dedicated chapter to writing data frame functions, I've 
compiled a compilation of resources for each topic I want us to cover. First, 
let's learn some of the "big picture" ideas of writing data frame functions.

### 📖 [Required Reading: *R4DS* -- Functions](https://r4ds.hadley.nz/functions#data-frame-functions)

::: callout-caution
# Read only Section 3 -- Data Frame Functions!
:::

### ✅  **Check-in 7.1 Writing Data Frame Functions** 

::: callout-note
# Data Structure

Note for these questions I am assuming the `flight` data has a similar
structure to the `nycflights` data from the openintro R package.

```{r}
#| echo: true
#| eval: false

head(openintro::nycflights)
```
:::

**Question 1**: Fill in the code below to write a function that finds all 
flights that were cancelled or delayed by more than a user supplied number of
hours:

```{r}
#| echo: true
#| eval: false

filter_severe <- function(df, hours) { 
  df |> 
    filter(dep_delay _____)
}


nycflights |> 
  filter_severe(hours = 2)
```

**Question 2**: Fill in the code below to write a function that converts the
user supplied variable that uses clock time (e.g., `dep_time`, `arr_time`, etc.)
into a decimal time (i.e. hours + (minutes / 60)).

```{r}
#| echo: true
#| eval: false


standardize_time <- function(df, time_var) {
  df |> 
    # Times are stored as 2008 for 8:08pm
    mutate( {{ time_var }} := 
              ## Grab first two numbers for hour
                str_sub(
                  ____, 
                  start = ____, 
                  end = ____) +  
              ## Grab second two numbers for minutes
                str_sub(
                  ____, 
                  start = ____, 
                  end = ____) / 60
            )
  
}

nycflights |> 
  standardize_time(arr_time)
```


# Tidy Selection & Data Masking

Now that we’ve learned how to write functions that operate on entire data
frames, we’re going to take this a step further and look more closely at tidy
evaluation---the system that powers how many tidyverse functions interpret and
evaluate your code.

At a high level:

- **Data masking** is used in functions that compute with variables, such as
`arrange()`, `filter()`, and `summarise()`. Inside these functions, you can
refer to column names directly (e.g., `filter(mpg > 20)`) because dplyr
temporarily "masks" the data frame’s columns so they behave like regular
variables.

- **Tidy selection** is used in functions that select variables, such as 
`select()` and `across()`. These functions let you choose columns using helpers
like `starts_with()`, `where(is.numeric)`, or vectors of column names.

A quick way to tell which system is in play:

- If the function accepts a **vector of column names** 
(e.g., `select(mtcars, c(vs, am, gear)))`, it uses tidy selection.

- If it does not accept a vector of column names and instead
**works on column values** (e.g., `filter(mtcars, mpg > 20))`, it uses data
masking.

Understanding which type of tidy evaluation a function uses will help you write
your own functions that behave just like tidyverse ones. 

Let's read this guide on tidy evaluation which breaks down what tidy selection
and data masking are and how they are used in dplyr functions. 

### 📖 [Programming with **dplyr**: Tidy Selection & Data Masking](https://dplyr.tidyverse.org/articles/programming.html)

::: {.column-margin}
**If you are interested in a video on tidy evaluation here is a talk by Jenny 
Bryan**
{{< video https://youtu.be/2BXPLnLMTYo?si=ry4tHOD77DWagvxn >}} 

::: {.callout-important}
I do want to note that this video is from 2019 and some things have changed 
since then. Namely, we used to need to use the `enquo()` function to inject
variable names into `dplyr` functions, whereas we now use embracing `{{}}`. 🤗
:::
:::

### ✅  **Check-in 7.2: Tidy Evaluation & Data Masking**

**Question 1:** Suppose you want to write a function that selects specific
columns from a data frame using a character vector of column names stored in 
`cols` (e.g., `cols = c("species", "bill_length_mm")`). Which of the following
code snippets will correctly select only those columns inside a function using
tidy selection?

```{r}
#| echo: true
#| eval: false

my_select <- function(df, cols) {
  # your code here
}
```

```{r}
#| echo: true
#| eval: false

## Option A
df %>% select(cols)

## Option B
df %>% select(all_of(cols))

## Option C
df %>% select({{ cols }})

## Option D
df %>% select(.data[[cols]])

```

<!-- (A) fails because select() interprets cols as a column name, not as a vector of names. -->

<!-- (B) is correct because tidy selection works with column-selection helpers and special functions like all_of() or any_of() when the names are stored as character vectors. -->

<!-- (C) fails because {{ cols }} is for data masking — unquoted symbols, not strings. -->

<!-- (D) fails because .data[[cols]] is used in data masking contexts (e.g., inside mutate() or filter()), not for selecting multiple columns. -->

**Question 2:** You’re writing a function that filters rows in a data frame based on a 
column specified by the user. The function should take the data frame (`df`), a 
column name (`var`), and a numeric threshold (`threshold`), and return all rows where
that column’s value is greater than the threshold. The function call should look
something like: `my_filter(penguins, bill_length_mm, 50)`

```{r}
#| echo: true
#| eval: false

my_filter <- function(df, var, threshold) {
  # your code here
}
```

```{r}
#| echo: true
#| eval: false

## Option A
df %>% filter(var > threshold)

## Option B
df %>% filter(.data[[var]] > threshold)

## Option C
df %>% filter({{ var }} > threshold)

## Option D
df %>% filter(df[[var]] > threshold)

```

<!-- (A) fails because filter() treats var literally (not as a variable referring to a column). -->

<!-- (B) fails because .data[[var]] is used when the column name is stored as a character string rather than a symbol. -->

<!-- (C) is correct because {{ var }} (the curly-curly or "embracing" syntax) is used for data masking—it allows you to use a column name passed as an unquoted argument inside a tidyverse verb. -->

<!-- (D) works in base R but not with dplyr’s data masking, which expects unquoted column references. -->

**Question 3**: For each of the following functions determine if the function
uses data-masking or tidy-selection:

-   `across()`
-   `count()`
-   `distinct()`
-   `group_by()`
-   `rename()`
-   `select()`

**Question 4**: Suppose I wanted to write a function that added a standardized
version of a specified (numeric) column into a data frame. Which of the
following functions would accomplish this task?

```{r}
#| echo: true
#| eval: false

## Option A
add_std_col <- function(df, var){
  mutate(df, 
         std_col = scale({{var}}, center = TRUE, scale = TRUE)
         )
}

## Option B
add_std_col <- function(df, var){
  mutate(df, 
         std_col = scale(var, center = TRUE, scale = TRUE)
         )
}

## Option C
add_std_col <- function(df, var){
  mutate(df, 
         std_col := scale({{var}}, center = TRUE, scale = TRUE)
         ) 
}

## Option D
add_std_col <- function(df, var){
  mutate(df, 
         std_col := scale(var, center = TRUE, scale = TRUE)
         )
}

```

<!-- (A) fails because you need to have a := to modify a variable -->
<!-- (B) fails because you need to use {{}} to grab the column AND you need := to modify the variable -->
<!-- (C) is correct because it uses := to modify the variable AND uses {{}} to grab the variable -->
<!-- (D) fails because you need to use {{}} to grab the column -->

**Question 5**: Suppose I wanted to scale my function from Question 4 into a
function that standardizes **every** numeric column from a specified data frame.
Which of the following functions would accomplish this task?

```{r}
#| echo: true
#| eval: false

## Option A
standardize_df <- function(df){
  mutate(df, 
         across(.cols = where(is.numeric), 
                .fns = ~ scale(.x, center = TRUE, scale = TRUE), 
                .names = "{.col}_std"
         )
         )
}

## Option B
standardize_df <- function(df){
  mutate(df, 
         across(.cols = pick(where(is.numeric)), 
                .fns = ~ scale(.x, center = TRUE, scale = TRUE), 
                .names = "{.col}_std"
         )
         )
}

## Option C
standardize_df <- function(df){
  mutate(df,
         std = scale(pick(where(is.numeric)), 
                     center = TRUE, 
                     scale = TRUE)
         )
}

## Option D
standardize_df <- function(df){
  mutate(df,
         across(.cols = where(is.numeric),
                .fns = ~ scale(pick(where(is.numeric)), 
                               center = TRUE, 
                               scale = TRUE),
      .names = "{.col}_std"
    )
  )
}
```

<!-- This question is all about whether or not to use pick().  -->
<!-- (A) is correct because where() selects the numeric columns using tidy select -->
<!-- (B) is incorrect because pick() returns a data frame and across() expects tidy selected columns  -->
<!-- (C) is incorrect because it hands all selected columns together to scale(), producing a matrix (or list-col) stuffed into one column std. The task is per-column standardization and should use across(). -->
<!-- (D) is incorrect because .fns function is called once per column and should operate on the vector .x. Instead, it ignores .x and passes a data frame of many columns (pick(...)) to scale().  -->
