---
title: "Writing Plotting Functions in R"
format: html
number-sections: true
number-depth: 2
bibliography: references.bib
editor: source
execute: 
  echo: true
  include: true
---

For the final part of this week, we are going to take what we've learned about data frame functions and create functions that produce visualizations.

### 📖 [Required Reading: *R4DS* -- Functions](https://r4ds.hadley.nz/functions#plot-functions)

::: callout-caution
# Read only Section 4 (Plot functions)!
:::

### ✅ **Check-in 7.3: Writing Plotting Functions**

**Question 1**: Fill in the code below to build a rich plotting function which:

-   draws a scatterplot given dataset and x and y variables,
-   adds a line of best fit (i.e. a linear model with no standard errors)
-   add a title.

```{r}
#| eval: false

labeled_scatterplot <- function(df, x_var, y_var) {
  
  label <- rlang::englue("A scatterplot of _____ and _____, including a line of best fit.")
  
  df |> 
    ggplot(mapping = aes(x = _____, 
                         y = _____
                         )
           ) + 
    geom_point() + 
    geom_smooth(method = "lm", _____) +
    labs(title = _____)
}
```

**Question 1**: Fill in the code below to build a rich plotting function which:

-   creates a barplot of the counts of each level of a categorical variable
-   sorts the bars in ascending order (smallest to largest)
-   capitalizes the names of the levels of the variable

```{r}
#| eval: false
#| echo: true

ascending_bars <- function(df, cat_var) {
  
  # To make the y-axis label of the 
  y_title <- as_label(enquo(cat_var))
  
  df |> 
    mutate(
      ## Order the levels based on the number of observations
      {{ cat_var }} := ____({{ cat_var }}),
      
      ## Relabel the levels to be capitalized 
      {{ cat_var }} := ____({{ cat_var }}, 
                            .fun = ~ str_to_title(.x)
                            )
           )  |>
    ggplot(aes(y = {{ cat_var }})) +
    geom_bar() +
    labs(x = "Number of Observations",
         y = str_to_title(y_title)
         )
}
```

<!-- (A) `fct_infreq` -- orders levels based on number of observations (largest first) -->
<!-- (B) `fct_relabel` -- uses a function to do the relabeling -->

::: callout-tip
You'll notice that I can't use `y = str_to_title({{ cat_var }})`. That is because the `labs()` function expects **string** inputs. So, I needed to transform the input variable (`cat_var`) into a string (e.g., "species").

Here is how this process works:

| Step | Code | Action |
|--------------|----------------------------|------------------|
| 1 | `ensym(cat_var)` | Turns the argument you passed into the function (e.g., `cat_var = species`) into the **symbol** `species`. |
| 2 | `as_label(ensym(cat_var))` | Turns the symbol `species` into the string `"species"` |
| 3 | `str_to_title(as_label(ensym(cat_var)))` | Capitalizes the string (`"species"` becomes `"Species"`) |
:::
