---
title: "Untitled"
---

## Use Variables within a Dataset

Suppose you would like for your `rescale()` function to perform operations on a **variable within a dataset**. Ideally, your function would take in a data
frame and a variable name as inputs and return a data frame where the variable
has been rescaled.

**8. Create a `rescale_column()` function that accepts two arguments:**

+ **a dataframe**
+ **the name(s) of the variable(s) to be rescaled**

**The body of the function should call the original `rescale_01()` function you wrote previously. Your solution MUST use one of the `rlang` options from class.**

::: callout-tip
If you are struggling with this task, I recommend looking back over the 
[data frame functions](https://r4ds.hadley.nz/functions.html#data-frame-functions)
section of R for Data Science!
:::

```{r}
#| label: rescale-data-frame-function

```

**9. Use your `rescale_column()` function to rescale *both* the `length` and `weight` columns.**

::: callout-warning
I expect that you carry out this process by calling the `rescale_column()` function only ONE time!
:::

```{r}
#| label: rescale-two-columns

```
