---
title: "Gallary of Exemplary Student Work"
execute: 
  warning: false
  message: false
  echo: true
---

```{r}
#| label: set-up-packages
#| echo: false

library(tidyverse)
library(ggtext)
```

# Challenge 2

Here are some of the exemplary assignments from your peers!

```{r}
#| label: data-for-lab-2
#| echo: false

surveys <- read_csv(here::here("labs",
                               "student",
                               "data", 
                               "surveys.csv")
                        )

```

## Themes

This code is brought to us by Jonathan Flores! I really appreciated the extensive themes they included and how these themes make the plot clearer to the reader.

```{r}
#| label: challenge-3-themes

ggplot(data = surveys,
    mapping = aes(x = species, y = weight)) +
  geom_boxplot(outliers = FALSE) +
  geom_jitter(color = "steel blue", alpha = 0.08) +
  labs(title = "Distribution of Weight by Species Boxplot",
       subtitle = "Vertical Orientation",
       x = "Species Name", y = "Weight (g)") + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45),
        axis.ticks.length.x = unit(8, "mm"),
        axis.ticks.x = element_line(color = "white"),
        panel.border = element_rect(color = "black", linewidth = 1),
        plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(color = "steelblue"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())
```

## Unique Colors

This code is brought to us by Fisher Fraley! I really appreciated how they found a unique color theme from a context they liked!

```{r}
# Color Palette: https://color.adobe.com/TRON-color-theme-6970180/
tron_colors <- c("#DF7212", "#6FC3DF", "#E6FFFF", "#FFE64D", "#0C141F")

ggplot(data = surveys, aes(x = weight, y = species, color = sex)) +
  geom_boxplot(outlier.shape = NA, width = 0.6) +
  geom_jitter(width = 0.15, height = 0, alpha = 0.3, size = 1) +
  scale_color_manual(values = tron_colors) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(
    title = "Rodent Weight by Species",
    subtitle = "Y-Axis = Rodent Species",
    x = "Rodent Weight (g)",
    y = NULL,
    caption = "Source: Portal Project Database"
   )
```

## Removing the Legend (and More)

This code is brought to us by Lucy Thackray! I thought it was special that Lucy stacked all three challenged to make a clean, easy to read plot.

```{r}
colors <- c("#f07857", "#4fb06d" )

ggplot(data = surveys,
       mapping = aes(x = weight, y = species)) +
  geom_jitter( alpha = 0.5) +
  geom_boxplot(outliers = FALSE, mapping = aes(color = sex)) +
  labs(x = "Weight (g)", y = "Species", color = "Sex",
       subtitle = "<span style = 'color:#f07857;'>Female</span> vs <span style = 'color:#4fb06d;'>Male</span> rodent species weights") +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
   theme(
    legend.position = "none", 
    plot.subtitle = element_markdown()) +
   theme(axis.ticks.y = element_blank()) +
scale_color_manual(values = colors)
```

# Lab 3

```{r}
#| label: data-for-lab-3
#| echo: false

library(knitr)

teacher_evals <- read_csv(here::here("labs", 
                                     "student",
                                     "data",
                                     "teacher_evals.csv")
                          )
```

## `across()` + `mutate()`

This code is brought to us by a student who wishes to remain anonymous! What I appreciated about this code was the use of `across()` when converting multiple columns to numeric. I also loved their use of the most current syntax for the `across()` function!

```{r}
teacher_evals_clean <- teacher_evals |>
  rename(sex = gender) |>
  mutate(teacher_id = as.character(teacher_id),
         question_no = as.character(question_no),
         across(
           .cols = c(no_participants, 
                     resp_share, 
                     SET_score_avg, 
                     percent_failed_cur, 
                     seniority),
           .fns = ~ as.numeric(.x)
           )
         )|>
  filter(no_participants > 10) |>
  select(course_id,
         teacher_id,
         question_no,
         no_participants,
         resp_share,
         SET_score_avg,
         percent_failed_cur,
         academic_degree,
         seniority,
         sex)
```

## Confirming Unique Row Identification

This code is brought to us by Akshat Khandelwal! I thought it was very clever how Akshat played with different combinations of variables to confirm which combination uniquely identified a row.

```{r}
#| echo: true

teacher_question <- teacher_evals |>
  distinct(teacher_id, question_no)

print(nrow(teacher_question) == nrow(teacher_evals))  # False

teacher_question_course <- teacher_evals |>
  distinct(teacher_id, question_no, course_id)

print(nrow(teacher_question_course) == nrow(teacher_evals))  # True

course_question <- teacher_evals |>
  distinct(question_no, course_id) 

print(nrow(course_question) == nrow(teacher_evals)) # False
```

## Proportions in Demographic Table

This code is brought to us by Arturo Ordaz-Gutierrez! I really appreciated how Art added the proportions to this demographic table so it is easier to see the representation of each group.

```{r}
#| echo: true

teacher_evals_clean |>
  distinct(teacher_id, .keep_all = TRUE) |>
  count(academic_degree, sex) |>
  mutate(percent = round(100 * n / sum(n), 1)) |>
  arrange(desc(percent))
```

## `across()` + `summarize()`

This code is brought to us by Rachel Survilas! I loved how Rachel noticed they were using the same `n_distinct()` function **across** multiple columns and decided to use `across()`! Also, the syntax they are using is on point!

```{r}
#| echo: true

teacher_evals_clean |> 
  summarize(
    across(
      .cols = c(teacher_id, course_id),
      .fns = ~ n_distinct(.x))
    )
```

## Demographic Barplots with Annotations

This code is brought to us by a student who wishes to remain anonymous! I thought this code was great because they chose to visualize the teacher demographics! They even added annotations to the top of their barplots!

```{r}
#| echo: true
#| layout-nrow: 1

individuals <- teacher_evals_clean |>
  group_by(teacher_id, sex, academic_degree, seniority) |> 
  summarise(n = n()) |> 
  ungroup()

individuals |> 
  group_by(sex) |> 
  summarise(n = n()) |> 
  ggplot(mapping = aes(x = sex, y = n)) +
  geom_col() +
      geom_text(aes(label = n), vjust = -0.5) +
      labs(x = "Sex", y = "Count")

individuals |> 
  group_by(seniority) |> 
  summarise(n = n()) |> 
  ggplot(mapping = aes(x = seniority, y = n)) +
  geom_col() +
      geom_text(aes(label = n), vjust = -0.5) +
      labs(x = "Seniority in Years", y = "Count")

individuals |> 
  group_by(academic_degree) |> 
  summarise(n = n()) |> 
  ggplot(mapping = aes(x = academic_degree, y = n)) +
  geom_col() +
      geom_text(aes(label = n), vjust = -0.5) +
      labs(x = "Academic Degree Held", y = "Count")
```

## Slicing the Max & Min Together

This code is brought to us by a student who wishes to remain anonymous! I thought this code was great because they got both the maximum values and the minimum values in **one** pipeline. Very efficient!

```{r}
#| echo: true

teacher_evals_clean |>
  filter(seniority == 1) |>
  group_by(teacher_id) |>
  summarize(
    avg_rating = mean(percent_failed_cur, na.rm = TRUE),
    .groups = "drop"
  ) |>
  filter(
    avg_rating == min(avg_rating)|
    avg_rating == max(avg_rating)
  ) |> 
  arrange(avg_rating)
```

## Using `kable()` for Nicer Looking Tables

This code is brought to us by a student who wishes to remain anonymous! I appreciated that they read the instructions to use the `kable()` function to get nicer looking tables. The code is very simple, but the tables look **much** nicer!

```{r}
#| echo: true

percent_failed <- teacher_evals_clean |> 
  group_by(teacher_id) |> 
  filter(seniority == 1) |> 
  summarize(avg_percent_failed = mean(percent_failed_cur))

percent_failed |> 
  slice_min(avg_percent_failed) |> 
  kable()
```

# Challenge 3

## Hypothesis Test Conclusion

These statements are brought to us by Abel Alcala and Sebastien Montgrain! I really appreciated the context they infused into their hypothesis test conclusion!

**Based on the results of the Chi-Squared test of Independence, we have a p-value of 0.006075 and a X\^2 value of 10.207. Since the p-value is less than α = 0.05, we reject the null hypotheses indicating a statistically significant association between seniority level and SET evaluation results. This suggests that instructor experience across junior, senior, and very senior appears to influence how students perceive the use of engaging activities in class.**

**Because the p-value of our Chi-squared test of independence is less than 0.05 (0.006075), we know that there is an association between a teachers seniority and their SET scores from question 3 on if the professor used activities to make the class more engaging. Combining this Chi-squared test with the graph, we can see that more experienced teachers do a better job of implementing engaging activities is their classes.**

# Challenge 4

```{r}
#| label: data-for-lab-4
#| echo: false

childcare_costs <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-09/childcare_costs.csv')

counties <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-09/counties.csv')

tax_rev <- read_csv('https://atheobold.github.io/groupworthy-data-science/labs/instructions/data/ca_tax_revenue.csv')

ca_childcare <- counties |>
  filter(state_name == "California") |>
  left_join(y = childcare_costs,
            join_by("county_fips_code")) |>
  left_join(y = tax_rev,
            join_by(county_name == entity_name,
                    study_year == year))

superior_counties <- c("Butte","Colusa","El Dorado",
                       "Glenn","Lassen","Modoc",
                       "Nevada","Placer","Plumas",
                       "Sacramento","Shasta","Sierra","Siskiyou",
                       "Sutter","Tehama","Yolo","Yuba")

north_coast_counties <- c("Del Norte","Humboldt","Lake",
                          "Mendocino","Napa","Sonoma","Trinity")

san_fran_counties <- c("Alameda","Contra Costa","Marin",
                       "San Francisco","San Mateo","Santa Clara",
                       "Solano")

n_san_joaquin_counties <- c("Alpine","Amador","Calaveras","Madera",
                            "Mariposa","Merced","Mono","San Joaquin",
                            "Stanislaus","Tuolumne")

central_coast_counties <- c("Monterey","San Benito","San Luis Obispo",
                            "Santa Barbara","Santa Cruz","Ventura")

s_san_joaquin_counties <- c("Fresno","Inyo","Kern","Kings","Tulare")

inland_counties <- c("Riverside","San Bernardino")

la_county <- "Los Angeles"

orange_county  <- "Orange"

san_diego_imperial_counties <- c("Imperial","San Diego")

ca_childcare <- ca_childcare |> 
  mutate(county_name = str_remove(county_name, " County"),
         census_region = fct_collapse(.f = county_name,
                                      `Superior California` = superior_counties,
                                      `North Coast` = north_coast_counties,
                                      `San Francisco Bay Area` = san_fran_counties,
                                      `North San Joaquin Valley` = n_san_joaquin_counties,
                                      `South San Joaquin Valley` = s_san_joaquin_counties,
                                      `Central Coast` = central_coast_counties,
                                      `Inland Empire` = inland_counties,
                                      `Los Angeles County` = la_county,
                                      `Orange County` = orange_county,
                                      `San Diego-Imperial` = san_diego_imperial_counties)
         )

```

## Amazing Tables

<!-- This table is brought to us by Shafay Syed! I thought their table stood out for -->
<!-- a few reasons. First, they are using `kable()` to get a nicely formatted HTML -->
<!-- table. Second, they gave their columns more intuitive names. Finally, they -->
<!-- organized / arranged the table in an intuitive way.  -->

```{r}
#| eval: false
#| echo: false

summary_table <- ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(census_region, study_year) |>
  summarise(
    center = median(mc_infant, na.rm = TRUE),
    family = median(mfcc_infant, na.rm = TRUE),
    .groups = "drop"
  ) |>
  pivot_wider(names_from = study_year, 
              values_from = c(center, family), 
              names_sep = "_") |>
  rename(
    region = census_region,
    `Gap 2018 (Center−Family)` = center_2018 - family_2018,
    `Center 2008` = center_2008,
    `Family 2008` = family_2008,
    `Center 2018` = center_2018,
    `Family 2018` = family_2018
  ) |>
  select(region, `Center 2008`, `Family 2008`, 
         `Center 2018`, `Family 2018`, `Gap 2018 (Center−Family)`) |>
  arrange(desc(`Center 2018`)) |>
  mutate(across(where(is.numeric), ~ round(.)))

knitr::kable(summary_table, 
             caption = "Median weekly infant prices (USD) by region and setting, 2008 vs 2018")
```

## Amazing Plots

This plot is brought to us by Marietta Nikolskaya! I was really excited to see 
someone create a "lollipop" plot, since they are what we (Statisticians) make
to compare how different a summary statistic is between groups. When plotting 
statistics like the mean, median, or difference, we generally advocate for this
type of plot over a barplot since barplots are typically reserved for plots of 
counts or proportions. 

```{r}
#| code-fold: true

# Here is the data wrangling that happened to make this plot!

ca_childcare_new <- ca_childcare |> 
  filter(study_year == 2018) |>
  select(census_region, mc_infant, mfcc_infant) |> 
  mutate(cost_difference = mc_infant - mfcc_infant) |>
  group_by(census_region) |>
  summarize(
    median_center = median(mc_infant),
    median_family = median(mfcc_infant),
    median_difference = median(cost_difference)) |>
  arrange(desc(median_difference))
```

```{r}
ca_childcare_new |>
  ggplot(aes(y = fct_reorder(census_region, median_difference), 
             x = median_difference)) +
  geom_segment(aes(yend = census_region, x = 0, xend = median_difference), 
               color = "gray50") +
  geom_point(size = 4, color = "steelblue") +
  labs(
    y = "",
    x = "Cost Difference: Center - Family ($)",
    title = "Cost Difference Between Center and Family Childcare for Infants (2018)"
  ) +
  theme_minimal()
```

This plot is brought to us by Devin Hadley! I thought this plot was really 
creative in their use of a non-standard geometry (`geom_ribbon()`) to fill the 
space between the lines. I also appreciated that they moved the legend to the 
top of the plot to make it easier to see! 

```{r}
#| code-fold: true

# Here is the data wrangling that happened to make this plot!
summary_table <- ca_childcare |>
  group_by(study_year) |>
  summarise(
    median_center_price = median(mc_infant),
    median_family_price = median(mfcc_infant)
  ) |>
  mutate(
    center_minus_family_price = median_center_price - median_family_price
  )

summary_table_long <- summary_table |>
  pivot_longer(
    cols = c("median_center_price", "median_family_price"),
    names_to = "care_type",
    values_to = "median_price"
  ) |>
  mutate(
    care_type = case_when(
      care_type == "median_center_price" ~ "Center-Based",
      care_type == "median_family_price" ~ "Family-Based",
      TRUE ~ care_type
    ))
```

```{r}
ggplot(summary_table_long, aes(x = study_year, y = median_price, color = care_type)) +
  geom_line(linewidth = 1.2) +
  geom_point(size = 3) +
  geom_ribbon(data = summary_table, aes(x = study_year, ymin = median_family_price, ymax = median_center_price, group = 1),
              fill = "skyblue", alpha = 0.3, inherit.aes = FALSE) +
  labs(
    title = "Median Weekly Infant Childcare Costs in California (2008-2018)",
    subtitle = "Based off the aggregated median price for each care type on an annual basis in various California counties.",
    x = "Year",
    y = "Median Weekly Price (2018 Dollars)",
    color = "Type of Childcare"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "top",
    plot.title = element_text(face = "bold"),
    plot.subtitle = element_text(margin = margin(b = 10)),
    axis.title = element_text(face = "bold"),
    plot.background = element_rect(color = "black", linewidth = 1) 
  )
```

This plot is brought to us by Isaiah Woodard! I really appreciated how Isaiah
took the skills they learned in Challenge 2 and applied them to a new setting!

```{r}
#| code-fold: true
# Here is the data wrangling that happened to make this plot!

plot_data <- ca_childcare %>% 
  select(census_region, study_year, mfccsa, mcsa) %>% 
  filter(study_year == c("2008":"2018")) %>% 
  group_by(census_region, study_year) %>% 
  summarise(median_mcsa = median(mcsa),
            median_mfccsa = median(mfccsa)) %>% 
  pivot_longer(cols = c(median_mcsa, median_mfccsa),
               names_to = "category",
               values_to = "medians")
```


```{r}
plot_data %>% 
  ggplot(aes(x = study_year,
             y = medians,
             color = category)) +
  facet_wrap(~ census_region) +
  geom_point() +
  scale_x_continuous(breaks = c(2008, 2010, 2012, 2014, 2016, 2018)) +
  labs(title = "Price of Childcare Over Time in California",
       subtitle = "Plots subdivided for <span style='color:#009e73;'>center-based</span> and <span     style='color:#d55e00;'>at-home</span> childcare",
       x = "Study Year",
       y = "Median Weekly Cost of Childcare ($)") +
  scale_color_manual(values = c("#009e73", "#d55e00")) +
  theme_bw() +
  theme(plot.subtitle = ggtext::element_markdown(),
        axis.text = element_text(size = 5),
        legend.position = "")
```

This plot is brought to us by Rayan Tahir! I thought Rayan's plot was very
clear and easy to understand. Moreover, their use of $ on the axis labels and
moving the legend to the top of the plot made it even easier to understand 
what was being plotted. 

```{r}
#| code-fold: true

# Here is the data wrangling that happened to make this plot!

ca_afford <- ca_childcare |>
  mutate(
    weekly_income = mhi_2018 / 52, 
    center_afford = mc_infant / weekly_income,
    family_afford = mfcc_infant / weekly_income
  )

ca_afford_long <- ca_afford |>
  select(study_year, center_afford,          family_afford) |>
  pivot_longer(
    cols = c(center_afford, family_afford),
    names_to = "Setting",
    values_to = "Affordability"
) |>
mutate(
  Setting = recode(Setting,
                  center_afford = "Center-Based",
                   family_afford = "Family-Based")
)
```

```{r}
ggplot(ca_afford_long, aes(x = study_year, y = Affordability, color = Setting)) +
  stat_summary(fun = median, geom = "line", linewidth = 1.2) +
  stat_summary(fun = median, geom = "point", size = 2.2) +
  scale_y_continuous(labels = scales::label_percent(accuracy = 1)) + 
  labs(
  title = "Affordability of Childcare in California (2008-2018)",
  subtitle = "Median Weekly Cost as a Share of County Median Household Income",
  x = "Year",
  y = "Median Share of Weekly Income Spent on Infant Care",
  color = "Childcare Setting"
) +
theme_minimal(base_size = 11) +
theme(
  plot.title = element_text(face = "bold", size = 15, hjust = 0.5),
  plot.subtitle= element_text(size = 12, hjust= 0.5),
  legend.position = "top"
)
```


<!-- # Lab 7 -->

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: data-for-lab-7

fish <- read_csv(here::here("labs", 
                            "instructions", 
                            "data", 
                            "BlackfootFish.csv")
                 )
```
