---
title: "Gallary of Exemplary Student Work"
execute: 
  warning: false
  message: false
  echo: true
---

```{r}
#| label: set-up-packages
#| echo: false

library(tidyverse)
library(ggtext)
```

# Challenge 2

Here are some of the exemplary assignments from your peers! 

```{r}
#| label: data-for-lab-2
#| echo: false

surveys <- read_csv(here::here("labs",
                               "student",
                               "data", 
                               "surveys.csv")
                        )

```

## Themes

This code is brought to us by Jonathan Flores! I really appreciated the extensive themes they included and how these themes make the plot clearer to the reader.

```{r}
#| label: challenge-3-themes

ggplot(data = surveys,
    mapping = aes(x = species, y = weight)) +
  geom_boxplot(outliers = FALSE) +
  geom_jitter(color = "steel blue", alpha = 0.08) +
  labs(title = "Distribution of Weight by Species Boxplot",
       subtitle = "Vertical Orientation",
       x = "Species Name", y = "Weight (g)") + 
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45),
        axis.ticks.length.x = unit(8, "mm"),
        axis.ticks.x = element_line(color = "white"),
        panel.border = element_rect(color = "black", linewidth = 1),
        plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(color = "steelblue"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())
```

## Unique Colors

This code is brought to us by Fisher Fraley! I really appreciated how they found a unique color theme from a context they liked! 

```{r}
# Color Palette: https://color.adobe.com/TRON-color-theme-6970180/
tron_colors <- c("#DF7212", "#6FC3DF", "#E6FFFF", "#FFE64D", "#0C141F")

ggplot(data = surveys, aes(x = weight, y = species, color = sex)) +
  geom_boxplot(outlier.shape = NA, width = 0.6) +
  geom_jitter(width = 0.15, height = 0, alpha = 0.3, size = 1) +
  scale_color_manual(values = tron_colors) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(
    title = "Rodent Weight by Species",
    subtitle = "Y-Axis = Rodent Species",
    x = "Rodent Weight (g)",
    y = NULL,
    caption = "Source: Portal Project Database"
   )
```

## Removing the Legend (and More)

This code is brought to us by Lucy Thackray! I thought it was special that Lucy stacked all three challenged to make a clean, easy to read plot. 

```{r}
colors <- c("#f07857", "#4fb06d" )

ggplot(data = surveys,
       mapping = aes(x = weight, y = species)) +
  geom_jitter( alpha = 0.5) +
  geom_boxplot(outliers = FALSE, mapping = aes(color = sex)) +
  labs(x = "Weight (g)", y = "Species", color = "Sex",
       subtitle = "<span style = 'color:#f07857;'>Female</span> vs <span style = 'color:#4fb06d;'>Male</span> rodent species weights") +
  theme_bw() +
  theme(panel.grid.minor = element_blank()) +
   theme(
    legend.position = "none", 
    plot.subtitle = element_markdown()) +
   theme(axis.ticks.y = element_blank()) +
scale_color_manual(values = colors)
```

<!-- # Lab 3 -->

```{r}
#| label: data-for-lab-3
#| echo: false
teacher_evals <- read_csv(here::here("labs", 
                                     "student",
                                     "data",
                                     "teacher_evals.csv")
                          )

# From student's lab
teacher_evals_clean <- teacher_evals |>
  rename(sex = gender) |>
  select(course_id,
         teacher_id,
         question_no,
         no_participants,
         resp_share,
         SET_score_avg,
         percent_failed_cur,
         academic_degree,
         seniority,
         sex
         ) |>
  mutate(
    course_id = as.factor(course_id),
    teacher_id = as.factor(teacher_id),
    sex = as.factor(sex),
    academic_degree = as.factor(academic_degree),
    question_no = as.integer(question_no)
  ) |>
  filter(no_participants >= 10)
```

<!-- # Lab 4 -->

```{r}
#| label: data-for-lab-4
#| echo: false

childcare_costs <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-09/childcare_costs.csv')

counties <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-09/counties.csv')

ca_childcare <- counties |>
  filter(state_abbreviation == "CA") |>
  inner_join(childcare_costs,
             by = "county_fips_code") %>% 
    mutate(region = fct_collapse(county_name,
                               `Superior California` = c("Butte County", 
                                                         "Colusa County", 
                                                         "El Dorado County", 
                                                         "Glenn County", 
                                                         "Lassen County", 
                                                         "Modoc County", 
                                                         "Nevada County", 
                                                         "Placer County", 
                                                         "Plumas County", 
                                                         "Sacramento County", 
                                                         "Shasta County", 
                                                         "Sierra County", 
                                                         "Siskiyou County", 
                                                         "Sutter County", 
                                                         "Tehama County", 
                                                         "Yolo County", 
                                                         "Yuba County"),
                               `North Coast` = c("Del Norte County", 
                                                 "Humboldt County", 
                                                 "Lake County", 
                                                 "Mendocino County", 
                                                 "Napa County", 
                                                 "Sonoma County", 
                                                 "Trinity County"),
                               `San Francisco Bay Area` = c("Alameda County", 
                                                            "Contra Costa County",
                                                            "Marin County",
                                                            "San Francisco County",
                                                            "San Mateo County",
                                                            "Santa Clara County",
                                                            "Solano County"),
                               `Northern San Joaquin Valley` = c("Alpine County",
                                                                 "Amador County",
                                                                 "Calaveras County",
                                                                 "Madera County",
                                                                 "Mariposa County",
                                                                 "Merced County",
                                                                 "Mono County", 
                                                                 "San Joaquin County",
                                                                 "Stanislaus County",
                                                                 "Tuolumne County"),
                               `Central Coast` = c("Monterey County", 
                                                   "San Benito County", 
                                                   "San Luis Obispo County", 
                                                   "Santa Barbara County", 
                                                   "Santa Cruz County",
                                                   "Ventura County"),
                               `Southern San Joaquin Valley` = c("Fresno County",
                                                                 "Inyo County", 
                                                                 "Kern County",
                                                                 "Kings County",
                                                                 "Tulare County"),
                               `Inland Empire` = c("Riverside County",
                                                   "San Bernardino County"),
                               `Los Angeles County` = c("Los Angeles County"),
                               `Orange County` = c("Orange County"),
                               `San Diego - Imperial` = c("Imperial County",
                                                          "San Diego County")
                               )
         )

```

<!-- # Lab 7 -->

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: data-for-lab-7

fish <- read_csv(here::here("labs", 
                            "instructions", 
                            "data", 
                            "BlackfootFish.csv")
                 )
```

