---
title: "Week 6 Day 1: Version Control"
format: docx
execute: 
  eval: false
---

# Lab 4 Review

```{r}
#| label: names-pivot
#| eval: false
#| echo: true

ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(region, study_year) |>
  summarise(median_income = median(mhi_2018, na.rm = TRUE)) |>
  pivot_wider(names_from = study_year, 
              values_from = median_income,
              names_prefix = "year_")

```

1.  What does the `names_prefix` argument do in the above code?

2.  What group variable(s) will remain after running the above code?

3.  Why would you want to reorder your facets?

4.  Why would you want to reorder your legend?

```{r}
#| label: nest-functions
#| eval: false
#| echo: true

mutate(age_group = fct_relevel(fct_recode(age_group,
                                          "Infant" = "mc_infant",
                                          "Toddler" = "mc_toddler",
                                          "Preschool" = "mc_preschool"),
                                "Infant",
                                "Toddler",
                                "Preschool"))
```

5.  What would improve the readability of the above code?

# Version Control

| Action | What it does | Steps in RStudio | Did you do this for your portfolio? |
|----|----|----|----|
| Fork | Copy someone else’s online project |  |  |
| Clone | Download a repo to your computer |  |  |
| Commit | Save your changes locally |  |  |
| Push | Upload your commits online |  |  |
| Pull | Download others’ updates |  |  |
