---
title: "Mathlink Activity"
---

# Piping

You can choose whether to: 

declare your data as the first argument of the function 
```{r}
#| echo: true
#| eval: false
#| code-line-numbers: false
#| label: not-piped-data

filter(.data = colleges, REGION == 5) |>
  mutate(TUITION_DIFF = TUITIONFEE_OUT - TUITIONFEE_IN)
```

***or***

pipe your data into the first argument of the function
```{r}
#| echo: true
#| eval: false
#| code-line-numbers: false
#| label: pipe-data

colleges |>
  filter(REGION == 5) |>
  mutate(TUITION_DIFF = TUITIONFEE_OUT - TUITIONFEE_IN)
```

# `filter`

**take your data frame and then filter it** (only include rows where) 

1. **the red column only includes observations with three sides** (triangles)

[OR]{.underline} 

2. **the green column only includes observations with more than four sides** (pentagons, hexagons)

# `select`

Step 1:

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: false

data |>
  select(red, 
         yellow, 
         green)
```

Step 2: 

```{r}
#| eval: false
#| echo: true
#| code-line-numbers: false

data |>
  select(-green)
```