---
title: "Midterm Portfolio Work Session"
format: 
  revealjs:
        theme: [simple, ../style.scss]
editor: source
---

```{r}
#| message: false
#| warning: false
#| echo: false

library(tidyverse)

if (!"purrr" %in% installed.packages()) install.packages("purrr")
source("https://raw.githubusercontent.com/zoerehnberg/STAT331-S23/main/challenges/bCH_murder_setup.R")
```

## When locating code...

> You can use **any** code from your Lab or Challenge assignments. 

-   find 1-2 **high quality** examples (quality \> quantity)
-   find examples that hit on **multiple** learning targets at the same time

## For example..

::: {.small}
the code below could be used to demonstrate proficiency with: 

::: columns
::: {.column width="45%"}
- WD-2 -- in two places (`select()` and `starts_with()`)!
- WD-7 -- pivoting longer
:::

::: {.column width="5%"}
:::

::: {.column width="50%"}
- WD-4 -- reordering a factor
- R-2 -- tidy dplyr pipeline
:::
:::

```{r}
#| echo: true
#| eval: false
#| label: example-student-code
#| code-line-numbers: false

ca_childcare |>
  select(study_year,
         mc_infant,
         mc_toddler,
         mc_preschool,
         region
         ) |>
  pivot_longer(cols = starts_with("mc_"), 
               names_to = "age", 
               values_to = "median_income"
               ) |> 
  mutate(age = fct_relevel(age, 
                          "mc_infant",
                          "mc_toddler",
                          "mc_preschool")
        )
```
:::

## `semi_join()` & `anti_join()`

> An Example from Lab 5...

::: columns
::: {.column width="50%"}
::: {.fragment}
::: {.small}
```{r}
#| echo: true
#| eval: true
#| code-line-numbers: false

new_suspect <- drivers_license |> 
  filter(height > 64, height < 68,
         hair_color == "red",
         gender == "female",
         car_make == "Tesla",
         car_model == "Model S") |>
  # rename column so keys match
  rename(license_id = id) |> 
  inner_join(person,
             by = "license_id") |> 
  inner_join(facebook_event_checkin,
             join_by(id == person_id)) |> 
  group_by(id, event_name) |> 
  count() |> 
  filter(event_name == "SQL Symphony Concert",
         n == 3)
```
:::
:::
:::

::: {.column width="5%"}
:::

::: {.column width="45%"}

::: {.fragment}
::: {.small}
```{r}
#| echo: true
#| eval: true
#| code-line-numbers: false

new_suspect
```
:::
:::
:::
:::

## `semi_join()` & `anti_join()`

> An Example from Lab 5...

::: {.midi}
```{r}
#| echo: true
#| code-line-numbers: false

interview |> 
  semi_join(new_suspect,
            by = join_by(person_id == id)) |> 
  pull(transcript)
```
:::

## Another way to think about it...

If there are lots of specific features you are looking for, you could put them
into a tibble (or a data frame). 

```{r}
#| echo: true
#| code-line-numbers: false

suspect_features <- tibble(
         hair_color = "red",
         gender = "female",
         car_make = "Tesla",
         car_model = "Model S")

```

## Another way to think about it...

You can then use these data as a **filtering join**! 

::: {.midi}
```{r}
#| echo: true
#| code-line-numbers: "3"
#| eval: false

drivers_license |> 
  filter(height > 64, height < 68) |>
  semi_join(suspect_features) |> 
  # rename column so keys match
  rename(license_id = id) |> 
  inner_join(person,
             by = "license_id") |> 
  inner_join(facebook_event_checkin,
             join_by(id == person_id)) |> 
  group_by(id, event_name) |> 
  count() |> 
  filter(event_name == "SQL Symphony Concert",
         n == 3)
```
:::

# Reflective Essays (not Lightening Round)

## Revising Your Thinking

- Where have you revised your code? 
- What have you learned by doing revisions? Be specific!
- How have you incorporated this knowledge into future assignments? Be specific!

## Extending Your Thinking 

- On what assignments did you push yourself by extending beyond what we learned
in class? 
- In what way? Be specific!

## Looking for examples?

</br>
</br>

The [Exemplary Student Work](https://atheobold.github.io/groupworthy-data-science/labs/exemplars/student-work.html) tab of the course website contains some exemplary code written
by your peers!

## Supporting Your Peers

::: {.midi}
- What have you learned about collaboration through the groupwork protocol?
  + How have you grown as a collaborator? Be specific!
- How have you supported your peers through code review?
  + Do you have a specific code review you are proud of? Show me! 
- Supporting your peers on Discord can look a variety of ways!
  + Did you ask questions that others could learn from?
  + Did you answer someone's question?
:::

# Determining Your Grade

## Determining Your Grade

> I believe my grade equivalent to course work evidenced below to be an __.

. . .

Your goal is to argue, convincingly and with concrete evidence, that you have
met the criteria that goes with a particular grade. 

. . .

This involves **every** part of the criteria--content proficiency, evidence of
continued learning, revising your thinking, and growth as a team member.

## Plus / Minus Modifiers

::: columns
::: {.column width="48%"}
::: {.fragment}
[**+**]{.larger}

::: {.midi}
- You’ve met all the criteria for the letter grade along with a significant
amount, but not all, of the criteria for the next letter grade up. 
:::
:::
:::

::: {.column width="4%"}
:::

::: {.column width="48%"}
::: {.fragment}
[**-**]{.larger}

::: {.midi}
- You have met the requirements for a letter grade but only in a way that you
believe is a bare minimum. 
- You’ve met almost all the requirements for the letter grade except for a small
number of minor criteria.
:::
:::
:::
:::


## What if you don't agree?

There are two ways this might happen.


::: columns
::: {.column width="48%"}
:::{.fragment}
::: {.small}
***You ask for a grade that is higher than the evidence supports.***

</br>

::: {.fragment}
That is, you grade yourself too highly. For example, you believe you earned an A
in the course, but I do not feel the evidence you’ve provided supports this
grade.

</br>

::: {.fragment}
In this case, I’ll tell you what grade I would have given you based on the
evidence you provided in the portfolio. You can then use this feedback when
constructing your Final Portfolio.
:::
:::
:::
:::
:::

::: {.column width="4%"}
:::

::: {.column width="48%"}
:::{.fragment}
::: {.small}
***You ask for a grade that was lower than your actual performance indicates.***

</br>

:::{.fragment}
That is, you "lowball" yourself, for example you say you earned a B when in fact
I think you earned an A-.

</br>

::: {.fragment}
In this case, I will tell you what grade I believe
you have earned and why.
:::
:::
:::
:::
:::
:::


# Midterm Portfolio Meetings

. . .

> Will occur on Tuesday and Wednesday of next week.

. . .

</br> 

Sign-up for your time here: [link to Google Sheet](https://docs.google.com/spreadsheets/d/1Lpstqy8YYs3MFzFNn2Kob7E289HyUJWxWpHkp1N_lJA/edit?usp=sharing)
