---
title: "Week 10 Extras"
format: revealjs
execute: 
  eval: false
---

<!-- ## In-line Code -->

<!-- We can automatically include code output in the written portion of a Quarto -->
<!-- document using `` `r` ``. -->

<!-- . . . -->

<!-- </br>  -->

<!-- ```{r} -->
<!-- #| code-line-numbers: false -->

<!-- my_rand <- rnorm(1, mean = 0, sd = 1) -->
<!-- my_rand -->
<!-- ``` -->

<!-- </br>  -->

<!-- Type this: My random number is `` `r knitr::inline_expr("my_rand")` ``. -->

<!-- To get this: My random number is `r my_rand`. -->

# Four Steps to Simualate Datasets

## Simulate Multiple Datasets - Step 1

::: {.small}
Write a function to simulate height data from a population with some mean and SD
height. 

The user should be able to input:

- how many observations to simulate
- the mean and standard deviation of the Normal distribution to use when 
simulating

::: {.callout-tip}
## Pencil out your function! 
:::
:::



::: columns
::: {.column width="60%"}
::: {.fragment}
::: {.small}
```{r}
#| code-line-numbers: false

sim_ht <- function(n = 200, avg, std){
  tibble(person = 1:n,
         ht = rnorm(n = n, mean = avg, sd = std))
}
```
:::
:::
:::

::: {.column width="5%"}
:::

::: {.column width="35%"}
::: {.fragment}
::: {.small}
```{r}
#| code-line-numbers: false

sim_ht(n = 5, 
        avg = 66, 
        std = 3)
```
:::
:::
:::
:::



## Simulate Multiple Datasets - Step 2

Create a set of parameters (mean and SD) for each population.

```{r}
#| code-line-numbers: false

crossing(mean_ht = seq(from = 60, to = 78, by = 6),
            std_ht  = c(3, 6))
```

## Simulate Multiple Datasets - Step 3

Simulate datasets with different mean and SD heights.

::: {.small}
```{r}
#| code-line-numbers: "4-7"

crossing(mean_ht = seq(from = 60, to = 78, by = 6),
         std_ht  = c(3, 6)
         ) |> 
 mutate(ht_data = pmap(.l = list(avg = mean_ht, std = std_ht), 
                       .f = sim_ht
                       )
        )
```
:::

. . .

::: {.small}
::: {.callout-tip}
# Why am I getting a tibble in the `ht_data` column?
:::
:::

## Simulate Multiple Datasets - Step 4

Extract the contents of each list!

::: {.small}
```{r}
#| code-line-numbers: "8"
#| eval: false

crossing(mean_ht = seq(from = 60, to = 78, by = 6),
         std_ht  = c(3, 6)
         ) |> 
 mutate(ht_data = pmap(.l = list(avg = mean_ht, std = std_ht), 
                       .f = sim_ht
                       )
        ) |> 
  unnest(cols = ht_data) |> 
  slice_sample(n = 10)
```
:::

::: columns
::: {.column width="50%"}
::: {.small}
```{r}
#| echo: false
#| eval: true

crossing(mean_ht = seq(from = 60, to = 78, by = 6),
         std_ht  = c(3, 6)
         ) |> 
 mutate(ht_data = pmap(.l = list(avg = mean_ht, std = std_ht), 
                       .f = sim_ht
                       )
        ) |> 
  unnest(cols = ht_data) |> 
  slice_head(n = 10)
```
:::
:::

::: {.column width="5%"}
:::

::: {.column width="45%"}
::: {.midi}
::: {.fragment}
Why do I now have `person` and `ht` columns?
:::

::: {.fragment}
How many rows should I have for each `mean_ht`, `std_ht` combo?
:::
:::
:::
:::

## `nest()` and `unnest()`

-   We can pair functions from the `map()` family very nicely with two `tidyr`
functions: `nest()` and `unnest()`.
-   These allow us to easily map functions onto subsets of the data.

## `nest()`

**Nest** subsets of the data (as tibbles) inside a tibble.

-   Specify the column(s) to create subsets on.

::: columns
::: {.column width="50%"}
```{r}
#| echo: true
#| code-line-numbers: false
#| eval: false

mtcars |> 
  nest(.by = cyl)
```
:::

::: {.column width="50%"}
```{r}
#| code-line-numbers: false
#| echo: false

mtcars |> 
  nest(.by = cyl)
```
:::
:::

## `unnest()`

**Un-nest** the data by row binding the subsets back together.

-   Specify the column(s) that contains the subsets.

::: columns
::: {.column width="40%"}
::: {.small}
```{r}
#| echo: true
#| eval: false
#| code-line-numbers: false

mtcars |> 
  nest(.by = cyl) |> 
  unnest(data) |> 
  slice_head(n = 10)
```
:::
:::

::: {.column width="5%"}
:::

::: {.column width="55%"}
::: {.small}
```{r}
#| echo: false
#| code-line-numbers: false

mtcars |> 
  nest(.by = cyl) |> 
  unnest(data) |> 
  slice_head(n = 10)
```
:::
:::
:::

## Simulate Multiple Datasets - Step 5

Plot the samples simulated from each population.

::: {.small}
```{r}
#| echo: false
#| code-line-numbers: false

fake_ht_data <- crossing(mean_ht = seq(from = 60, to = 78, by = 6),
         std_ht  = c(3, 6)
         ) |> 
 mutate(ht_data = pmap(.l = list(avg = mean_ht, std = std_ht), 
                       .f = sim_ht
                       )
        ) |> 
  unnest(cols = ht_data)
```

```{r}
#| code-fold: true
#| fig-width: 8
#| fig-height: 4
#| fig-align: center

fake_ht_data |> 
  mutate(across(.cols = mean_ht:std_ht, 
                .fns = ~as.character(.x)), 
         mean_ht = fct_recode(mean_ht, 
                              `Mean = 60` = "60", 
                              `Mean = 66` = "66", 
                              `Mean = 72` = "72", 
                              `Mean = 78` = "78"), 
         std_ht = fct_recode(std_ht, 
                             `Std = 3` = "3", 
                             `Std = 6` = "6")
         ) |> 
  ggplot(mapping = aes(x = ht)) +
  geom_histogram(color = "white") +
  facet_grid(std_ht ~ mean_ht) +
  labs(x = "Height (in)",
       y = "",
       subtitle = "Frequency of Observations",
       title = "Simulated Heights from Eight Different Populations")
```
:::

