---
title: "Lab 8: Data Frame Functions + Fish"
author: "Instructions"
format: 
  html:
    toc: true
editor: source
execute: 
  error: true
  echo: true
  eval: false
  message: false
  warning: false
---

## Use Variables within a Dataset

Suppose you would like for your `rescale()` function to perform operations on a **variable within a dataset**. Ideally, your function would take in a dataframe and a variable name as inputs and return a dataframe where the variable has been rescaled.

**8. Create a `rescale_column()` function that accepts two arguments: (1) a dataframe and (2) the name(s) of the variable(s) to be rescaled. The body of the function should call the original `rescale_01()` function you wrote previously. Your solution MUST use one of the `rlang` options from class.**

::: callout-tip

If you are struggling with this task, I recommend looking [here](https://rlang.r-lib.org/reference/topic-defuse.html) and  at the slides from class on Wednesday!

:::

```{r}
# Code for Q8.
```

**9. Use your `rescale_column()` function to rescale *both* the `length` and `weight` columns.**

::: callout-warning

I expect that you carry out this process by calling the `rescale_column()` function only ONE time!

:::

```{r}
# original values
fish |> 
 select(length:weight) |> 
 head()

# rescaled values

# Code for Q9.

```
